\section{Literature protocol}\label{sec:literature-protocol}

In the literature, when we need to develop a new project, there is a protocol which should be followed to increase the possibility of success.
This protocol is composed by different steps, the success of every step is fundamental for the prosecution of the next steps.
The steps are:
\begin{enumerate}
    \item Study of the state of the art and deepening about the other projects' results.
    \item Seeking for the dataset, we should look for a dataset which is adatto to our purpose, we should understand the characteristics of the datasets.
    \item We should then find some projects in oder to use them for the comparison
    \item Validate the dataset using the other models, trying to reach the same results as the ...
    \item Establish a baseline as the model.
    \item Overfit the model with a single prediction target, in our case a single sequence to verify the network capacity, but ...
    \item Overfit the model with two and more prediction target, in this way, we are verifying that the model can learn more than one target, which is usefull for us to understand which is the limit of the network in term of capacity.
    \item Train the model with the whole dataset, trying to improve the results achieved by the baseline.
    \item We can also change the structure of the neural network.
    \item Fine-gtuning, perform a fine tuning of the neural network can squeeze the last drops of performance of the network.
    \item
\end{enumerate}